### 2022-03-22 paper/output/document/thesis_3_implementation.tex
i hate don knuth

I implement this definition in Isabelle by defining the \texttt{type\_synonym} below for the type
of a maxim.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{A maxim is of type term, open sentence, term tuple, such as ``(When I am strapped for cash, will falsely promise
to repay a loan, to get some easy cash)''. The first term represents the circumstance, which
can be true or false at a world. For example, the circumstance ``when I am strapped for cash'' is true at the real 
world when my bank account is empty. The second term represents the act, which is an open sentence
because different agents can perform a particular action. For example, the act, ``will falsely promise
to repay a loan'' is an open sentence that can be acted on by a subject. The third term represents 
the goal, which can again be true or false at a world. For example, the goal ``to get some easy cash''
is true at the real world if I have successfully received easy cash.%
}%
\begin{isamarkuptext}%
O'Neill argues that a maxim 
is an action-guiding rule and thus naturally includes an act and the circumstances under which 
it should be performed \citep[37]{actingonprinciple}. 
She also includes a purpose, end, or goal in the maxim because human activity is guided by a rational will
and is thus inherently purposive \citep[40]{groundwork}. A rational will does not act randomly (else it would not be rational), 
but instead in the pursuit of ends which it deems valuable. The inclusion a maxim's end is essential 
for the version of the FUL that I will implement, explained in Section \ref{praccon}.

@@

\begin{definition}[Willing]\label{willing}
For maxim $M = (C, A, G)$ and actor $s$,
$$\text{\emph{will}} \, M \, s \equiv \forall w \, (C \longrightarrow A \, (s)) \, w$$
\noindent At all worlds $w$, if the circumstances hold at that world, agent $s$ performs act $A$.
\end{definition}

@@

This view cannot correctly handle natural acts. Korsgaard appeals to 
\citet{dietrichson} to construct the example natural act of a mother killing her children that
cry too much at night so that she can get some sleep. Thought this maxim is clearly wrong, universalizing 
it does not generate a logical contradiction because killing is still possible in a world where 
everyone kills noisy children. Because killing is a natural act, it can never be logically 
impossible so the logical contradiction view cannot prohibit it.

As an alternative to the logical contradiction view, Korsgaard endorses the practical contradiction view, 
which prohibits maxims that are self-defeating, or ineffective, when universalized. By willing a maxim, 
you commit yourself to the maxim's goal, and thus cannot rationally will that this goal be 
undercut. This interpretation can prohibit natural acts like those of the sleep-deprived mother: in 
willing the end of sleeping, she is implicitly willing that she is alive. If all mothers kill all 
loud children, then she cannot be secure in the possession of her life, because her own mother may 
have killed her as an infant. Her willing this maxim thwarts the end that she sought to secure.

@@

\includegraphics[scale=0.6]{goalstable.png}

@@

\noindent \textbf{Obligation Universalizes Across People} The obligations prescribed by the Formula of Universal Law

@@

%:%187=102%:%

@@

%:%230=145%:%
%:%231=145%:%

@@

%:%234=147%:%

@@

%:%245=152%:%
%:%257=154%:%

@@

%:%310=208%:%
%:%311=208%:%

@@

%:%314=210%:%

@@

%:%318=213%:%

@@

%:%337=233%:%
%:%338=233%:%

@@

%:%341=235%:%

@@

%:%345=240%:%

@@

%:%357=252%:%
%:%358=252%:%

@@

%:%361=254%:%
%:%364=256%:%

@@

%:%398=290%:%
%:%399=290%:%

@@

%:%402=292%:%

@@

%:%404=293%:%

@@

%:%406=294%:%

@@

%:%409=296%:%

@@

%:%413=298%:%

@@

%:%418=303%:%
%:%419=303%:%

@@

%:%422=305%:%

@@

%:%424=306%:%

@@

%:%426=307%:%
%:%428=308%:%

@@

%:%438=312%:%
%:%450=314%:%

@@

%:%459=324%:%
%:%460=324%:%
%:%462=325%:%

@@

%:%468=330%:%

@@

%:%471=333%:%
%:%472=333%:%
%:%474=333%:%
%:%478=333%:%
%:%479=333%:%

@@

%:%481=334%:%
%:%482=334%:%
%:%491=336%:%

@@

%:%516=361%:%
%:%517=361%:%

@@

%:%520=363%:%

@@

%:%524=366%:%
%:%526=368%:%
%:%527=368%:%

@@

%:%530=370%:%

@@

%:%532=371%:%

@@

%:%535=373%:%

@@

%:%537=374%:%
%:%539=374%:%
%:%543=374%:%
%:%544=374%:%
%:%546=375%:%

@@

%:%562=383%:%

@@

%:%584=405%:%
%:%585=405%:%
%:%587=407%:%

@@

%:%600=413%:%
%:%612=415%:%

@@

%:%639=443%:%

@@

%:%647=450%:%

@@

%:%660=461%:%

@@

%:%675=476%:%
%:%676=476%:%

@@

%:%680=478%:%
%:%684=478%:%
%:%685=478%:%
%:%687=479%:%

@@

%:%690=481%:%
%:%692=482%:%

@@

%:%701=485%:%
%:%704=486%:%

@@

%:%706=487%:%

@@

%:%710=489%:%
%:%714=489%:%
%:%715=489%:%
%:%717=490%:%

@@

%:%728=493%:%

@@

%:%751=516%:%
%:%752=516%:%

@@

%:%756=518%:%
%:%760=518%:%
%:%761=518%:%
%:%762=518%:%
%:%764=519%:%
%:%770=519%:%
%:%773=520%:%

@@

%:%775=521%:%

@@

%:%780=524%:%
%:%784=524%:%
%:%785=524%:%
%:%786=524%:%
%:%788=525%:%

@@

%:%800=529%:%

@@

%:%809=539%:%
%:%810=539%:%
%:%813=540%:%
%:%817=540%:%
%:%818=540%:%
%:%820=541%:%

@@

%:%822=542%:%
%:%824=543%:%
%:%834=545%:%

@@

%:%843=554%:%
%:%844=554%:%

@@

%:%849=557%:%
%:%853=557%:%
%:%854=557%:%
%:%855=557%:%
%:%857=558%:%

@@

%:%860=560%:%
%:%862=561%:%

@@

%:%874=565%:%

@@

%:%877=568%:%
%:%878=568%:%

@@

%:%883=571%:%
%:%887=571%:%
%:%888=571%:%
%:%889=571%:%
%:%891=572%:%
%:%892=572%:%
%:%894=573%:%

@@

%:%905=576%:%

@@

%:%922=593%:%

@@

%:%933=603%:%

@@

>>>>

I implement this definition in Isabelle by defining the \texttt{type\_synonym} below for the type
of a maxim.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%
\ maxim\ {\isacharequal}\ {\isachardoublequoteopen}{\isacharparenleft}t\ {\isacharasterisk}\ os\ {\isacharasterisk}\ t{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{A maxim is of type term, open sentence, term tuple, such as ``(When I am strapped for cash, will falsely promise
to repay a loan, to get some easy cash)''. The first term represents the circumstance, which
can be true or false at a world. For example, in the \nameref{falsepromise} maxim, the circumstance
``when I am strapped for cash'' is true at the real 
world when my bank account is empty. The second term represents the act, which is an open sentence
because different agents can perform a particular action. For example, the act, ``will falsely promise
to repay a loan'' is an open sentence that can be acted on by a subject. The third term represents 
the goal, which can again be true or false at a world. For example, the goal ``to get some easy cash''
is true at the real world if I have successfully received easy cash.%
}%
\begin{isamarkuptext}%
O'Neill argues that a maxim 
is an action-guiding rule and thus naturally includes an act and the circumstances under which 
it should be performed \citep[37]{actingonprinciple}. 
She also includes a purpose, end, or goal in the maxim because human activity is guided by a rational will
and is thus inherently purposive \citep[40]{groundwork}. A rational will does not act randomly (else it would not be rational), 
but instead in the pursuit of ends which it deems valuable. The inclusion a maxim's end is essential 
for the version of the FUL that I will implement, explained in Section \ref{praccon}.

@@

\begin{definition}[Willing]\label{willing}
For maxim $M = (C, A, G)$ and actor $s$,
$$\text{\emph{will}} \, M \, s \equiv \forall w \, (C \longrightarrow A \, (s)) \, w$$
\noindent At all worlds $w$, if the circumstances hold at that world, actor $s$ performs act $A$.
\end{definition}

@@

This view cannot correctly handle natural acts, or acts that are possible simply due to the laws of nature. Korsgaard appeals to 
\citet{dietrichson} to construct the example natural act of a mother killing her children that
cry at night so that she can get some sleep. Thought this maxim is clearly wrong, universalizing 
it does not generate a logical contradiction because killing is still possible in a world where 
everyone kills noisy children. Because killing is a natural act, it can never be logically 
impossible so the logical contradiction view cannot prohibit it.

As an alternative to the logical contradiction view, Korsgaard endorses the practical contradiction view, 
which prohibits maxims that are self-defeating, or ineffective, when universalized. By willing a maxim, 
you commit yourself to the maxim's goal, and thus cannot rationally will that this goal be 
undercut. This interpretation can prohibit natural acts like those of the sleep-deprived mother: in 
willing the end of sleeping, she is implicitly willing that she is alive. If all mothers kill all 
loud children, then she cannot be secure in the possession of her life, because her own mother may 
have killed her when she cried as an infant. Her willing this maxim thwarts the end that she sought to secure.

@@

\includegraphics[scale=0.165]{goalstable.jpeg}

@@

\noindent \textbf{Obligations Universalize Across People} The obligations prescribed by the Formula of Universal Law

@@

%:%185=101%:%

@@

%:%229=144%:%
%:%231=146%:%

@@

%:%233=147%:%

@@

%:%238=151%:%
%:%246=153%:%

@@

%:%309=206%:%
%:%311=209%:%

@@

%:%313=210%:%

@@

%:%316=212%:%

@@

%:%336=231%:%
%:%338=234%:%

@@

%:%340=235%:%

@@

%:%343=237%:%

@@

%:%356=251%:%
%:%358=253%:%

@@

%:%360=254%:%
%:%362=255%:%

@@

%:%397=289%:%
%:%399=291%:%

@@

%:%401=292%:%

@@

%:%404=294%:%

@@

%:%406=295%:%

@@

%:%408=296%:%

@@

%:%411=298%:%

@@

%:%417=302%:%
%:%419=304%:%

@@

%:%421=305%:%

@@

%:%424=307%:%

@@

%:%426=308%:%
%:%427=308%:%

@@

%:%431=311%:%
%:%439=313%:%

@@

%:%458=322%:%
%:%460=325%:%
%:%461=325%:%

@@

%:%466=329%:%

@@

%:%470=332%:%
%:%472=334%:%
%:%473=334%:%
%:%475=334%:%
%:%479=334%:%

@@

%:%481=335%:%
%:%482=335%:%
%:%483=335%:%

@@

%:%515=360%:%
%:%517=362%:%

@@

%:%519=363%:%

@@

%:%522=365%:%
%:%525=367%:%
%:%527=369%:%

@@

%:%529=370%:%

@@

%:%532=372%:%

@@

%:%535=374%:%

@@

%:%537=375%:%
%:%538=375%:%
%:%540=375%:%
%:%544=375%:%
%:%545=375%:%

@@

%:%553=382%:%

@@

%:%583=404%:%
%:%585=406%:%
%:%586=406%:%

@@

%:%592=412%:%
%:%601=414%:%

@@

%:%637=440%:%

@@

%:%645=449%:%

@@

%:%657=460%:%

@@

%:%674=475%:%
%:%676=477%:%

@@

%:%678=478%:%
%:%681=479%:%
%:%685=479%:%
%:%686=479%:%

@@

%:%690=482%:%
%:%691=482%:%

@@

%:%696=486%:%
%:%702=486%:%

@@

%:%706=488%:%

@@

%:%708=489%:%
%:%711=490%:%
%:%715=490%:%
%:%716=490%:%

@@

%:%719=492%:%

@@

%:%750=515%:%
%:%752=517%:%

@@

%:%754=518%:%
%:%757=519%:%
%:%761=519%:%
%:%762=519%:%
%:%763=519%:%
%:%765=520%:%
%:%771=520%:%

@@

%:%775=522%:%

@@

%:%778=524%:%
%:%781=525%:%
%:%785=525%:%
%:%786=525%:%
%:%787=525%:%

@@

%:%791=528%:%

@@

%:%808=537%:%
%:%810=540%:%
%:%811=540%:%
%:%814=541%:%
%:%818=541%:%
%:%819=541%:%

@@

%:%822=543%:%
%:%823=543%:%
%:%825=544%:%

@@

%:%842=553%:%
%:%844=555%:%

@@

%:%847=557%:%
%:%850=558%:%
%:%854=558%:%
%:%855=558%:%
%:%856=558%:%

@@

%:%860=561%:%
%:%861=561%:%

@@

%:%865=564%:%

@@

%:%876=567%:%
%:%878=569%:%

@@

%:%881=571%:%
%:%884=572%:%
%:%888=572%:%
%:%889=572%:%
%:%890=572%:%
%:%892=573%:%
%:%893=573%:%

@@

%:%896=575%:%

@@

%:%919=590%:%

@@

%:%930=601%:%

@@

%:%959=629%:%

### 2022-03-22 paper/output/document/thesis_4_applications.tex
i hate don knuth

In this chapter, I tackle this challenge by endowing my system with this kind of common sense in the 
specific case of lying. While my system has the ability to reason
using the Formula of Universal Law, this reasoning must be applied to objects that are defined
using common sense. Because common sense facts can determine my system's judgements, they are part of the trusted
code base for my system, or the logic and code that a user must trust in order to trust my system. 
Malicious common sense facts will result in bad judgements.
For example, if we define truth telling as an act that is self-contradictory (perhaps
by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
system, and virtually all prior attempts in machine ethics face similar challenges. Many prior attempts
sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.

@@

This concludes my examination of the maxim of lying to a liar. I was able to show that, by
modifying the common sense facts used, my system can show that lying to a liar is permissible, but lying 

>>>>

In this chapter, I tackle this challenge by automating this kind of common sense in the 
specific case of lying. While my system has the ability to reason
using the Formula of Universal Law, this reasoning must be applied to objects that are defined
using common sense. Because common sense facts can determine my system's judgements, they are part of the trusted
code base for my system, or the logic and code that a user must trust in order to trust my system. 
Malicious common sense facts will result in bad judgements.
For example, if we define truth telling as an act that is self-contradictory (perhaps
by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
system, and virtually all prior attempts in machine ethics face similar challenges. Many prior attempts
sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.

@@

This concludes my examination of the maxim of lying to a liar. I was able to show that, given minimal
common sense facts, my system shows that lying to a liar is permissible, but lying 
